Semistochastic importance sampling of second-quantized operators in determinant space: application to multireference perturbation theory

### 2021-06-01 notes/paper.tex
Small change

Most of the time, for values of $N$ that are not trivially small, Alias sampling would be the preferred choice of these two sampling algorithms as it has a lower time complexity per sample.

However, as we will describe below, CDF searching has an intriguing use case: Suppose we want to be able to sample one of the first $n$ elements of a stored discrete distribution, where $n$ is not known ahead of time. In that case, we could modify the sampling algorithm to sample only one of the first $n$ elements by simply multiplying $r$ by $\textrm{CDF}_n$ before binary-searching. In that case, the setup time would be negligible! Alias sampling does not have an analogous property.

>>>>

\subsubsection{Both sampling algorithms are useful}
Most of the time, for values of $N$ that are not trivially small, Alias sampling would be the preferred choice of these two sampling algorithms as it has a lower time complexity per sample.

However, as we will describe below, CDF searching has an intriguing use case: Suppose we want to be able to sample one of the first $n$ elements of a stored discrete distribution, where $n$ is not known ahead of time. In that case, we could modify the sampling algorithm to sample only one of the first $n$ elements by simply multiplying $r$ by $\textrm{CDF}_n$ before binary-searching, so the setup time is negligible! Alias sampling does not have an analogous property, so we need both sampling algorithms to perform the sampling described in this paper.
